Towards a miniKanren with fair search strategies

### 2019-05-22 Paper/paper.tex
trivial
g_

\lstset{
  language=Scheme,
  basicstyle=\ttfamily,
  morekeywords={run,conde,run*,defrel,==,fresh,disj,conj,disj+},
  alsodigit={!\$\%&*+-./:<=>?@^_~},
  morecomment=[l]{;,\#{}lang},
  mathescape=true,
  literate={-inf}{{$^\infty$}}{1} {/fair}{{$_{fair}$}}{3}
  		   {→}{{$\rightarrow$}}{1}
  		   {×}{{$\times$}}{1}
  		   {==}{{$\equiv$}}{1}
  		   {conde}{{\textcolor[rgb]{0,.3,.7}{\textbf{cond$^e$}}}}{4}
  		   {repeato}{{repeat$^o$}}{6}
}
%% scheme-list .

>>>>

\lstset{
  language=Scheme,
  basicstyle=\ttfamily,
  morekeywords={run,conde,run*,defrel,==,fresh,disj,conj,disj+},
  alsodigit={!\$\%&*+-./:<=>?@^_~},
  morecomment=[l]{;,\#{}lang},
  mathescape=true,
  literate={-inf}{{$^\infty$}}{1} {/fair}{{$_{fair}$}}{3}
  		   {→}{{$\rightarrow$}}{1}
  		   {×}{{$\times$}}{1}
  		   {==}{{$\equiv$}}{1}
  		   {conde}{{\textcolor[rgb]{0,.3,.7}{\textbf{cond$^e$}}}}{4}
  		   {repeato}{{repeat$^o$}}{6}
  		   {g0}{{g$_0$}}{1}
  		   {g1}{{g$_1$}}{1}
  		   {g2}{{g$_2$}}{1}
  		   {gl}{{g$_l$}}{1}
  		   {gr}{{g$_r$}}{1}
}
%% scheme-list .
